You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-29 paper/paper.tex
incorporated wei's feedback

\section{Introduction}
%The plays of William Shakespeare and their \emph{modern} translations are treated
%as parallel text which is used to learn paraphrase models targeting the style of Early Modern English employed by Shakespeare.

@@

\subsection{Baselines}
Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04chen11}, however this approach does require the existence of
parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
quantify the benefit of access to parallel text in the source and target styles.

@@

To build a phrase table, we scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}; 
example dictionary entries are presented in table \ref{dictionary_example}. 
As described in \cite{Koehn00}, we estimate phrase translation probabilities
based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
We obtained the conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 
36 plays by SRILM toolkit \cite{Stolcke02} \ref{word_frequency}, 
normalizing the probabilities for each source phrase, for example $p(\text{PERCHANGE}|\text{maybe}) = \frac{0.0000790755}{0.00026264791} = 0.30107035689$. 
This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
with a language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet), which are then fed into the Moses decoder
\cite{Koehn07}.

@@

\subsubsection{Out of Domain Monolingual Parallel Text}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of domain parallel text, with an in-domain
language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
Although this monolingual parallel data does not include text in the target writing style,
the in-domain language model does bias the system's output towards Shakespeare's style of writing.
We found that performing Minimum Error Rate Training using a small set of held out parallel text from Romeo and Juliet was necessary in order to tune the
video corpus baseline to generate reasonable paraphrases.

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT} instead of using the default Moses parameters.\\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model. a\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean Paraphrase.  Romeo and Juliet is held out for testing.}
  \label{systems}
\end{table}

@@

\bibliographystyle{apa}

\bibliography{paper.bib}

>>>>

\newpage
\section{Introduction}
%The plays of William Shakespeare and their \emph{modern} translations are treated
%as parallel text which is used to learn paraphrase models targeting the style of Early Modern English employed by Shakespeare.

@@

\subsection{Baselines}
Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04,chen11}, however this approach does require the existence of
parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
quantify the benefit of access to parallel text in the source and target styles.

@@

To build a phrase table, we scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}; 
example dictionary entries are presented in table \ref{dictionary_example}. 
As described in \cite{Koehn00}, we estimate phrase translation probabilities
based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
We obtained the conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 
36 plays by SRILM toolkit \cite{Stolcke02} \ref{word_frequency}, 
normalizing the probabilities for each source phrase, for example $p(\text{PERCHANGE}|\text{maybe}) = \frac{0.0000790755}{0.00026264791} = 0.30107035689$. 
This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
with a language model consisting of Shakespeare's 36 plays (holding out {\em Romeo and Juliet}), which are then fed into the Moses decoder
\cite{Koehn07}.

@@

\subsubsection{Out of Domain Monolingual Parallel Data}
\label{video_baseline}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of domain parallel text, with an in-domain
language model consisting of Shakespeare's 36 plays (holding out {\em Romeo and Juliet} for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
Although this monolingual parallel data does not include text in the target writing style,
the in-domain language model does bias the system's output towards Shakespeare's style of writing.
We found that performing Minimum Error Rate Training using a small set of held out parallel text from Romeo and Juliet was necessary in order to tune the
video corpus baseline to generate reasonable paraphrases.

@@

\subsection{Examples}
Several example paraphrases of lines from {\em Romeo and Juliet} and several Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.

\begin{table}
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT} instead of using the default Moses parameters.\\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
      in detail in section \ref{video_baseline}. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean Paraphrase.  {\em Romeo and Juliet} is held out for testing.}
  \label{systems}
\end{table}

@@

\bibliographystyle{apa}
\bibliography{paper}
